Deterministic contention management for low latency Cloud RAN over an optical ring

### 2019-01-28 v3/articleV3.tex
modifs format
majuscule

\usepackage{color}
\usepackage{amsmath}
%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
\captionsetup{justification=centering,margin=0.5cm}

@@

        \begin{center}
      \hspace{-2.3cm}\includegraphics[scale=0.65]{containers}

@@

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.7]{interface.pdf}
     \caption{Insertion of C-RAN traffic in the N-GREEN optical ring.}\label{fig:interface}

\end{center}
  \end{figure}

\paragraph{Best effort traffic}

@@

We compare experimentally these two methods in the simplest topology: The lengths of the arcs between nodes are equal and there is one RRH by node. The experimental parameters are given in Table~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}. In each experiment, the offsets of the RRHs are drawn uniformly at random in the period. The results are computed over $1,000$ experiments in which the optical ring is simulated during $1,000,000$ units of time. Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods. The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
   \vspace{-1cm}
        \begin{center}
      \includegraphics[scale=0.3]{opport.pdf}
         \vspace{-1cm}
     \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}

\end{center} 
\begin{figure}[h]
\begin{minipage}[t]{.46\linewidth}
  \scalebox{.55}
  {
  \begin{tabular}{|c|c|}
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
    Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Container size  $C$ & $100$ kb  \tabularnewline
  \hline
  Unit of time (UoT) $C/(F\times R)$ & $1~\mu$s \tabularnewline
  \hline
  Length traveled during one UoT & $200$ m \tabularnewline
  \hline
    \end{tabular}
  }

@@

\end{center}
  \end{figure}

@@

The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node has access to a container from a free position, as shown in Fig.~\ref{fig:slotbal}. To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas using the previous strategy. Then, set the $x$ used positions in the following way: $\lfloor\frac{F}{x}\rfloor -1 $ free positions are set between each used positions. If $\frac{F}{x}$ has a reminder $r$, then we set the $r$ free remaining positions uniformly over the interval in the same way and so on until there are no more free position. It is a small optimization, since it decreases the latency by at most $F/2$.

\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.55]{repart1}
     \caption{Balancing used positions.}\label{fig:slotbal}

\end{center}
  \end{figure}

  \paragraph{Experimental evaluation}

@@

@@

As shown in Fig.\ref{fig:algocmp}, the performance of the naive assignment is really bad. Compacting the RRHs on a minimal number of positions decreases dramatically the latency. If in addition, we balance over a period, we get another gain of latency of smaller magnitude: the average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $3.28 \mu$s (resp. $37 \mu$s).
We did not represent the benefit of balancing used positions because the reduction in latency it yields is small as expected: The average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $4.43 \mu$s (resp. $44 \mu$s).

@@

\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.25]{periodonly}
     \caption{BE latencies of a naive assignment and balancing inside the period for $5$ antennas.}  
     \label{fig:periodonly}
  \end{center}
  \end{figure}

\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.25]{repart1res}
     \caption{BE latencies of compacting positions and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
\end{center}
  \end{figure}
  \begin{figure}[h]
\begin{center}   
     \includegraphics[scale=0.25]{optim.pdf}
     \caption{FIFO buffer compared to the best method with reservation for $12$ antennas.} \label{fig:optimres}
\end{center}
  \end{figure}

@@

 The $(l+1)$th RRH emits up to time $P - \omega(u_{l+1},u_{0})$ at position zero, so that there is no conflict with RRH $0$ during the next period.
 Hence, it has used the position zero during $x = P - \omega(u_{l+1},u_{0}) - l*ET - \omega(u_0,u_{l+1}) = P - l*ET - RS$. From time $P - \omega(u_{l+1},u_{0}) + 2$, the $(l+1)$th RRH emits at position $2$ and during a time $ET - x$. Then the next RRH in the order is assigned to position $2$, and begins to emit at time $P - \omega(u_{l+1},u_{0}) + ET -x$ instead of zero. The rest of the assignment is built in the same way filling completely all first positions, until there are no more RRH.  
\end{proof}

@@

\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.8]{split}
     \caption{Valid assignment for $9$ antennas and the N-GREEN parameters.}   \label{fig:split}
\end{center}
  \end{figure}

@@

\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.25]{splitres}
     \caption{Latencies of saturating positions, balancing into the period and FIFO rule for 5 antennas.}   \label{fig:splitres}
\end{center}
  \end{figure}

>>>>

\usepackage{color}
\usepackage{amsmath}
%\usepackage[colorlinks=true,breaklinks=true,linkcolor=blue]{hyperref}
\captionsetup{justification=centering,margin=0.5cm}
\usepackage[pscoord]{eso-pic}
\newcommand{\placetextbox}[3]{
\setbox0=\hbox{#3} 
\AddToShipoutPictureFG*{ 
\put(\LenToUnit{#1\paperwidth},\LenToUnit{#2\paperheight}){ 
\vtop{{\null}\makebox[0pt][c]{#3}}}
}
}
\placetextbox{.2}{0.055}{XXX-X-XXXXX-XX-X~\copyright~2018 IFIP}

@@

        \begin{center}
   \includegraphics[scale=0.65]{containers}

@@

\begin{figure}[h!]
\begin{center}  
      \includegraphics[scale=0.7]{interface.pdf}
     \caption{Insertion of C-RAN traffic in the N-GREEN optical ring.}\label{fig:interface}
\end{center}
  \end{figure}
\vspace{-0.5cm}
\paragraph{Best effort traffic}

@@

We compare experimentally these two methods in the simplest topology: The lengths of the arcs between nodes are equal and there is one RRH by node. The experimental parameters are given in Table~\ref{fig:params} and chosen following~\cite{ngreenarchitecture}. In each experiment, the offsets of the RRHs are drawn uniformly at random in the period. The results are computed over $1,000$ experiments in which the optical ring is simulated during $1,000,000$ units of time. Fig.~\ref{fig:resultopport} gives the cumulative distribution of both C-RAN and BE traffics latencies for the FIFO and the C-RAN priority methods. The source code in C of the experiments can be found on one of the authors' webpage~\cite{webpage}.
   \vspace{-1.3cm}
   \begin{figure}[h]
        \begin{center}
      \includegraphics[scale=0.3]{opport.pdf}
         \vspace{-1cm}
     \captionof{figure}{Distribution of latencies for FIFO and C-RAN first}    \label{fig:resultopport}

\end{center} 
\end{figure}
   \vspace{-1cm}
\begin{figure}[h]
\begin{minipage}[t]{.46\linewidth}
  \scalebox{.55}
  {
  \begin{tabular}{|c|c|}
  \hline
  Bit rate of an electronic interface $R$ & $10$ Gbps \tabularnewline
  \hline
  Optical ring bit rate $F\times R$ & $100$ Gbps \tabularnewline
  \hline
    Acceleration factor $F$ & $10$  \tabularnewline
  \hline
  Container size  $C$ & $100$ kb  \tabularnewline
  \hline
  Unit of time (UoT) $C/(F\times R)$ & $1~\mu$s \tabularnewline
  \hline
  Length traveled during one UoT & $200$ m \tabularnewline
  \hline
    \end{tabular}
  }

@@

\end{center}
  \end{figure}  
     \vspace{-0.4cm}

@@

The free positions can be distributed uniformly over a slot, to minimize the time to wait before a node has access to a container from a free position, as shown in Fig.~\ref{fig:slotbal}. To do so, compute the number of needed positions $x = \lceil k\times \frac{ET}{P - RS}\rceil$, with k the number of antennas using the previous strategy. Then, set the $x$ used positions in the following way: $\lfloor\frac{F}{x}\rfloor -1 $ free positions are set between each used positions. If $\frac{F}{x}$ has a reminder $r$, then we set the $r$ free remaining positions uniformly over the interval in the same way and so on until there are no more free position. It is a small optimization, since it decreases the latency by at most $F/2$.
     \vspace{-0.4cm}
\begin{figure}[h!]
\begin{center}   
      \includegraphics[scale=0.55]{repart1}
     \caption{Balancing used positions.}\label{fig:slotbal}
\end{center}
  \end{figure}
     \vspace{-0.4cm}
  \paragraph{Experimental evaluation}

@@

       \vspace{-0.4cm}
\begin{figure}[h!]
\begin{center}

      \includegraphics[scale=0.25]{periodonly}
     \caption{BE latencies of a naive assignment and balancing inside the period for $5$ antennas.}  
     \label{fig:periodonly}
  \end{center}
  \end{figure}
    \vspace{-0.4cm}

@@

As shown in Fig.\ref{fig:algocmp}, the performance of the naive assignment is really bad. Compacting the RRHs on a minimal number of positions decreases dramatically the latency. If in addition, we balance over a period, we get another gain of latency of smaller magnitude: the average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $3.28 \mu$s (resp. $37 \mu$s).
We did not represent the benefit of balancing used positions because the reduction in latency it yields is small as expected: the average (respectively maximum) latency for BE traffic goes from $4.76 \mu$s (resp. $48 \mu$s) to $4.43 \mu$s (resp. $44 \mu$s).

\begin{figure}[h!]
\begin{center}   
      \includegraphics[scale=0.25]{repart1res}
     \caption{BE latencies of compacting positions and balancing inside the period for $12$ antennas.}   \label{fig:algocmp}
\end{center}
  \end{figure}

@@

  \begin{figure}[h!]
\begin{center}   
     \includegraphics[scale=0.25]{optim.pdf}
     \caption{FIFO buffer compared to the best method with reservation for $12$ antennas.} \label{fig:optimres}
\end{center}
  \end{figure}

@@

 The $(l+1)$th RRH emits up to time $P - \omega(u_{l+1},u_{0})$ at position zero, so that there is no conflict with RRH $0$ during the next period.
 Hence, it has used the position zero during $x = P - \omega(u_{l+1},u_{0}) - l*ET - \omega(u_0,u_{l+1}) = P - l*ET - RS$. From time $P - \omega(u_{l+1},u_{0}) + 2$, the $(l+1)$th RRH emits at position $2$ and during a time $ET - x$. Then the next RRH in the order is assigned to position $2$, and begins to emit at time $P - \omega(u_{l+1},u_{0}) + ET -x$ instead of zero. The rest of the assignment is built in the same way filling completely all first positions, until there are no more RRH.  
\end{proof}
 \vspace{-0.4cm}
\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.8]{split}
     \caption{Valid assignment for $9$ antennas and the N-GREEN parameters.}   \label{fig:split}
\end{center}
  \end{figure}
  \vspace{-0.4cm}

@@

 \vspace{-0.4cm}
\begin{figure}[h]
\begin{center}

      \includegraphics[scale=0.25]{splitres}
     \caption{Latencies of saturating positions, balancing into the period and FIFO rule for 5 antennas.}   \label{fig:splitres}
\end{center}
  \end{figure}
    \vspace{-0.4cm}

@@
